MIGRACE DAT - DEMUS / MUSEION

### 2023-02-13 R_BIOLIB_slovniky.Rmd
BioLib slovniky

path_mdb <-  "M:/02 dokumenty/03 migrace/"

@@

dbname <- paste0(path_mdb, "BIO_slovniky.accdb") # path to database
con <- RODBC::odbcConnectAccess2007(dbname)      # set the connection

@@

kmen <- RODBC::sqlFetch(con, "PRM_BioLib_080_Animalia_Kmen")
trida <- RODBC::sqlFetch(con, "PRM_BioLib_090_Animalia_Trida")  
rad <- RODBC::sqlFetch(con, "PRM_BioLib_100_Animalia_Rad")  
celed <- RODBC::sqlFetch(con, "PRM_BioLib_110_Animalia_Celed")  
rod <- RODBC::sqlFetch(con, "PRM_BioLib_130_Animalia_Rod")  
druh <- RODBC::sqlFetch(con, "PRM_BioLib_150_Animalia_Druh")  
poddruh <- RODBC::sqlFetch(con, "PRM_BioLib_153_Animalia_Poddruh")

@@

>>>>

path_mdb <-  "M:/03 klienti/kraj moravskoslezsky/muzeum beskyd - MUZBE/"

# NACTENI BIOLIB SLOVNIKU (KK sum)

```{r BIOLIB DICT}

biolib <- read.table(paste0(path, "BioLib_KKsummary.csv"), sep = ";", header = T)

@@

dbname <- paste0(path_mdb, "01 muzBE analyza/PVO/Databaze_PVO_2021-11-03.accdb") # path to database
con <- RODBC::odbcConnectAccess2007(dbname, pwd = "Fazole")      # set the connection

@@

zoo <- RODBC::sqlFetch(con, "Pz_System_ZOOpredmety")

@@

write.table(join6, paste0(path, "BioLib_KKsummary.csv"), sep = ";", row.names = F)
